\documentclass[11pt, journal]{IEEEtran}

\usepackage[pdftex]{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{filecontents}
\usepackage[noadjust]{cite}

\begin{filecontents*}{references.bib}
@inproceedings{ray1999determination,
  title={Determination of number of clusters in k-means clustering and application in colour image segmentation},
  author={Ray, Siddheswar and Turi, Rose H},
  booktitle={Proceedings of the 4th international conference on advances in pattern recognition and digital techniques},
  pages={137--143},
  year={1999}
}
@inproceedings{raniwala2005architecture,
  title={Architecture and algorithms for an IEEE 802.11-based multi-channel wireless mesh network},
  author={Raniwala, Ashish and Chiueh, Tzi-cker},
  booktitle={INFOCOM 2005. 24th Annual Joint Conference of the IEEE Computer and Communications Societies. Proceedings IEEE},
  volume={3},
  pages={2223--2234},
  year={2005},
  organization={IEEE}
}
\end{filecontents*}

\begin{document}
\title{Fancy title here}

\author{Harsh~Damania, Christophe~Faucon, Nicolas~Salhuana, Tsung-Yen~Yu}

\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
With today's technology, there are a number of different smartphone apps out there that try to be an all in one social network, and many that play around with the users location to provide data. We take this concept of combining niche location based social networking services, and add a twist with dynamic location data. Users are classified in to zones based on where other app users are right now and can thus communicate with those around, which could end up being for special events.
\end{abstract}

\begin{IEEEkeywords}
social networking, location services, clustering
\end{IEEEkeywords}}

\maketitle
\IEEEdisplaynotcompsoctitleabstractindextext

\section{Introduction}
	\IEEEPARstart{I}{n} today's day and age where technology keeps changing and new ideas are born on a daily basis, there are still a lot of holes left to plug in various areas of computing. There has been a tremendous success of mobile apps in the areas of social networking and location based services, and there have been quite a few that combine these 2 disciplines. Our project provides a little a twist to these 2 disciplines to make it different from other apps, and make it better for people on the go.

	\subsection{Project Description}
		Our project is location based social network. There can a lot be done with a users location, and thus we chose to use this location data to group a user within a zone with other app users. The size of the zone is determined by the number of other app users around. While in a zone, the user can then send messages to others within the same zone and discuss and what's happening near by. This app would help users understand if there is something special on nearby, and also help understand the events in the zone.
	
	\subsection{The Need}

		The main use of the app would be for the social networking and getting to know what is going on around you at a given time. There have been a number of other mobile apps that have gained traction lately that relate to social networking and location based services, but none quite have a good blend of the 2 that can be used on the go.

		The use of a location service where a user is automatically allocated to a zone they are in based on ``hotspots''. This way a user who is new to the area can instantly tell what is going on at the moment based on where other app users are and see if there is anything special going on.

		Another noteworthy use of the app is for getting a live feed of the current event in a ``hotspot''. For example, for a college football game, there could be a large number of users in around the stadium that form a zone and everyone within that zone can talk and discuss about the game on that thread. Users are stored within a zone 24 hours after they have left it if they wanted to discuss the thread for a little while after the event too.

\section{Related Work}
\input{relatedWork.tex}

\section{Goals}
	For our project, we had 3 main goals that we wanted to accomplish
	\begin{itemize}
		\item Ability for the user to be assigned a zone automatically based on location: We wanted to make sure that the user would be allocated into their zone based on where the other app users were. This further determined zones for future users to connect to. This was the heart of the project.
		\item Users should be able send messages to others in their zones: The entire point of being allocated in a zone is for the users to see what others around them are discussing. Since this is a part social network, it is integral for the user to communicate with others.
		\item Setup a centralized server with Zone messages: Our project will rely on a centralized service that a user can GET and POST to. Joining a zone, downloads the messages on to the users device.
	\end{itemize}

\section{System Model and Problem Statement}
\input{systemModel.tex}

\section{Approach}
\input{approach.tex}

\section{Implementation}
\input{implementation.tex}

\section{Results}
\input{results.tex}

\section{Conclusion}
\input{conclusion.tex}

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
	